% BoxGeom

\section{\class{BoxGeom} ---
         Box geometry}

\begin{classdesc}{BoxGeom}{lx=1.0, ly=1.0, lz=1.0, segmentsx=1, segmentsy=1, segmentsz=1}

\var{lx}, \var{ly} and \var{lz} specify the dimensions of the box in
the respective direction.

\var{segmentsx}, \var{segmentsy} and \var{segmentsz} are the number of
segments in each direction.
\end{classdesc}

A \class{BoxGeom} has the following slots:

\begin{tableiv}{l|l|c|l}{code}{Slot}{Type}{Access}{Description}
\lineiv{cog_slot}{vec3}{r}{The local center of gravity}
\lineiv{inertiatensor_slot}{mat3}{r}{The local inertia tensor}
\lineiv{lx_slot}{float}{rw}{The length in x direction}
\lineiv{ly_slot}{float}{rw}{The length in y direction}
\lineiv{lz_slot}{float}{rw}{The length in z direction}
\lineiv{segmentsx_slot}{int}{rw}{The number of segments in x direction}
\lineiv{segmentsy_slot}{int}{rw}{The number of segments in y direction}
\lineiv{segmentsz_slot}{int}{rw}{The number of segments in z direction}
\end{tableiv}

% Attributes
\begin{memberdesc}{cog}
Center of gravity with respect to the local coordinate system.
\end{memberdesc}

\begin{memberdesc}{inertiatensor}
Inertia tensor with respect to the local coordinate system.
\end{memberdesc}

\begin{memberdesc}{lx}
The length in x direction.
\end{memberdesc}

\begin{memberdesc}{ly}
The length in y direction.
\end{memberdesc}

\begin{memberdesc}{lz}
The length in z direction.
\end{memberdesc}

\begin{memberdesc}{segmentsx}
The number of segments in x direction.
\end{memberdesc}

\begin{memberdesc}{segmentsy}
The number of segments in y direction.
\end{memberdesc}

\begin{memberdesc}{segmentsz}
The number of segments in z direction.
\end{memberdesc}







