% CCylinderGeom

\section{\class{CCylinderGeom} ---
         Capped cylinder geometry}

\begin{classdesc}{CCylinderGeom}{radius=1.0, length=1.0, segmentsu=16, segmentsvl=1, segmentsvr=4}

\var{radius} is the radius of the cylinder and caps in the local coordinate 
system.

\var{length} is the length of the cylinder (not counting the caps).

\var{segmentsu} is the number of segments in u direction, \var{segmentsvl}
the number of segments of the cylinder part and \var{segmentsvr} the
number of segments for each cap.
\end{classdesc}

A \class{CCylinderGeom} has the following slots:

\begin{tableiv}{l|l|c|l}{code}{Slot}{Type}{Access}{Description}
\lineiv{cog_slot}{vec3}{r}{The local center of gravity}
\lineiv{inertiatensor_slot}{mat3}{r}{The local inertia tensor}
\lineiv{radius_slot}{float}{rw}{The radius of the cylinder}
\lineiv{length_slot}{float}{rw}{The lenght of the cylinder}
\lineiv{segmentsu_slot}{int}{rw}{The number of segments in u direction}
\lineiv{segmentsvl_slot}{int}{rw}{The number of cylinder segments in v direction}
\lineiv{segmentsvr_slot}{int}{rw}{The number of cap segments in v direction}
\end{tableiv}

% Attributes
\begin{memberdesc}{cog}
Center of gravity with respect to the local coordinate system.
\end{memberdesc}

\begin{memberdesc}{inertiatensor}
Inertia tensor with respect to the local coordinate system.
\end{memberdesc}

\begin{memberdesc}{radius}
The radius of the cylinder and caps.
\end{memberdesc}

\begin{memberdesc}{length}
The length of the cylinder (not counting the caps).
\end{memberdesc}

\begin{memberdesc}{segmentsu}
The number of segments in u direction.
\end{memberdesc}

\begin{memberdesc}{segmentsvl}
The number of cylinder segments in v direction.
\end{memberdesc}

\begin{memberdesc}{segmentsvr}
The number of cap segments in v direction.
\end{memberdesc}
