% cgkit manual
% Creating HTML: mkhowto --html tex/cgkit.tex

\documentclass{manual}
\usepackage{graphicx}

\title{Python Computer Graphics Kit}

\author{Matthias Baas}
\authoraddress{
        Email: \email{baas@ira.uka.de}
}

%\date{May 20, 2004}            % XXX update before final release!
\date{\today}
%---------------------------------------------------------
% Version information
\release{2.0.0alpha6}
\setreleaseinfo{}
\setshortversion{2.0}
%---------------------------------------------------------

\makeindex                      % tell \index to actually write the
                                % .idx file
\makemodindex                   % ... and the module index as well.

%---------------------------------------------------------
\begin{document}

\maketitle

\ifhtml
\chapter*{Front Matter\label{front}}
\fi

Copyright \copyright{} 2004 Matthias Baas.
All rights reserved.

The RenderMan\textregistered Interface Procedures and Protocol are:
Copyright \copyright{} 1988, 1989, 2000, Pixar.
All Rights Reserved.

RenderMan\textregistered is a registered trademark of Pixar.

See the end of this document for complete license and permissions
information.

\begin{abstract}

\noindent
The Python Computer Graphics Kit is a generic 3D package written in
C++ and Python that can be used for a variety of domains such as
scientific visualization, photorealistic rendering, Virtual Reality or
even games.  The package contains a number of generic modules that can
be useful for any application that processes 3D data. This includes
new types such as vectors, matrices and quaternions. Furthermore, the
package can read and store 3D models in memory where they can be
manipulated by Python programs. The kit comes with tools that can be
used to display the scene either interactively or by rendering it
offline via a RenderMan renderer.
\end{abstract}

%---------------------------------------------------------

\tableofcontents

%---

\chapter{Introduction \label{introduction}}

\input{introduction.tex}

%---

\chapter{Building \& Installing \label{build}}

\input{building.tex}

%---

\chapter{Tools \label{tools}}

\input{viewer.tex}
\input{render.tex}

%---

\chapter{Generic modules \label{modules1}}

\localmoduletable

\input{cgkitinfo.tex}
\input{cgtypes.tex}
\input{ri.tex}
\input{riutil.tex}
\input{noise.tex}
\input{sl.tex}
\input{sltokenize.tex}
\input{slparams.tex}
\input{glslangtokenize.tex}
\input{glslangparams.tex}
\input{spacedevice.tex}
\input{wintab.tex}
\input{glove.tex}
\input{asfamc.tex}
\input{bvh.tex}
\input{objmtl.tex}
\input{mayaascii.tex}
\input{lwob.tex}
\input{hammersley.tex}
\input{stitch.tex}

%---

\chapter{Scene specific modules \label{modules2}}

\localmoduletable

\input{pluginmanager.tex}
\section{\module{scene} --- }
\input{eventmanager.tex}
\input{events.tex}
\input{keydefs.tex}
\section{\module{preferences} --- }
\section{\module{undo} --- }
\input{slots.tex}

%---
\chapter{Commands \label{commands}}
\input{cmds.tex}

%---
\chapter{The scene\label{scene}}

\input{scene.tex}
\input{sceneglobals.tex}

%---
\chapter{Components \label{components}}

\declaremodule{}{cgkit}

This chapter lists all available components.

%\localmoduletable

\input{component.tex}
\input{timer.tex}
\input{euleradapter.tex}
\input{expression.tex}
\input{lookat.tex}
\input{valuetable.tex}
\input{tunnel.tex}
\input{odedynamics.tex}
\input{flockofbirds.tex}
\input{gnuplotter.tex}
\input{pidcontroller.tex}
\input{slideshow.tex}
\input{motionpath.tex}

%---
\chapter{WorldObjects \label{worldobjects}}

\input{worldobject.tex}
\input{box.tex}
\input{sphere.tex}
\input{ccylinder.tex}
\input{plane.tex}
\input{torus.tex}
\input{trimesh.tex}
\input{polyhedron.tex}
\input{group.tex}
\input{joint.tex}
\input{targetcamera.tex}
\input{freecamera.tex}
\input{glpointlight.tex}
\input{gltargetspotlight.tex}
\input{glfreespotlight.tex}
\input{gltargetdistantlight.tex}
\input{glfreedistantlight.tex}
\input{spotlight3ds.tex}
\input{mayaspotlight.tex}
\input{rmlightsource.tex}
\input{ribarchive.tex}
\input{odejoints.tex}
\input{beziercurve.tex}


%---
\chapter{GeomObjects \label{geomobjects}}

\input{geomobject.tex}
\input{boxgeom.tex}
\input{spheregeom.tex}
\input{ccylindergeom.tex}
\input{planegeom.tex}
\input{torusgeom.tex}
\input{trimeshgeom.tex}
\input{polyhedrongeom.tex}
\input{beziercurvegeom.tex}

%---
\chapter{Materials \label{materials}}

\input{glmaterial.tex}
\input{rmmaterial.tex}
\input{material3ds.tex}
\input{objmaterial.tex}

%---
\chapter{Auxiliary classes \label{auxclasses}}

\input{boundingbox.tex}
\input{joystick.tex}


%---
\chapter{Plugins \label{plugins}}

\section{Export plugins}
\input{ribexport.tex}
\input{offexport.tex}
\input{objexport.tex}
\input{plyexport.tex}

\section{Import plugins \label{importplugins}}
\input{pyimport.tex}
\input{offimport.tex}
\input{3dsimport.tex}
\input{vrmlimport.tex}
\input{ifsimport.tex}
\input{objimport.tex}
\input{maimport.tex}
\input{stlimport.tex}
\input{asfamcimport.tex}
\input{bvhimport.tex}
\input{plyimport.tex}

%---------------------------------------------------------

\appendix

%\chapter{Reporting Bugs}
%\input{reportingbugs}

\chapter{License}
\input{license.tex}

%
%  The ugly "%begin{latexonly}" pseudo-environments are really just to
%  keep LaTeX2HTML quiet during the \renewcommand{} macros; they're
%  not really valuable.
%

%begin{latexonly}
\renewcommand{\indexname}{Module Index}
%end{latexonly}
\input{modcgkit.ind}              % Module Index

%begin{latexonly}
\renewcommand{\indexname}{Index}
%end{latexonly}
\input{cgkit.ind}                 % Index

\end{document}
