% FlockOfBirds component

\section{\class{FlockOfBirds} ---
         Retrieving values from an Ascension Flock of Birds\textsuperscript{\textregistered} motion tracker}

The \class{FlockOfBirds} class communicates with an Ascension Flock
of Birds\textsuperscript{\textregistered} motion tracker 
(\url{http://www.ascension-tech.com/}) via the serial port and provides the 
sensor values of the individual birds via slots.

Note: Currently, the class assumes that an extended range controller is
used! (this means the position values have to be adjusted if you use the
tracker without an extended range controller)

\begin{classdesc}{FlockOfBirds}{name = "FlockOfBirds",\\ 
                                com_port = 0,\\
                                baud_rate = 115200,\\
                                timeout = 2.0,\\
                                num_birds = 1,\\
                                bird_mode = "p",\\
                                hemisphere = "forward",\\
                                auto_insert = True}


\var{com_port} specifies which COM port to use for the communication with
the flock (0-based port number).

\var{baud_rate} is the baud rate to use.

\var{timeout} specifies a time span in seconds after which a RS232 operation
fails.

\var{num_birds} is the number of birds to use (including the ERC which will 
be bird 1).

\var{bird_mode} selects what kind of data the birds will send. It can be either
a string containing the mode for all birds or it can be a list of strings
to select a mode for each individual bird. In the latter case, the list must
hold one string for each bird. The mode string can be one of the values
in the following table:

\begin{tableii}{c|l}{code}{Mode}{Description}
\lineii{"p"}{Send only the position.}
\lineii{"a"}{Send only euler angles.}
\lineii{"m"}{Send only a rotation matrix.}
\lineii{"q"}{Send only a quaternion.}
\lineii{"pa"}{Send position and euler angles.}
\lineii{"pm"}{Send position and matrix.}
\lineii{"pq"}{Send position and quaternion.}
\end{tableii}

\var{hemisphere} specifies in which hemisphere, centered about the
transmitter, the sensor will be operating (see the {\em Flock of Birds ---
Installation and Operation Guide}). The values can be one of \code{"forward"},
\code{"aft"}, \code{"upper"}, \code{"lower"}, \code{"left"} and \code{"right"}.

\end{classdesc}


For each bird, the \class{FlockOfBirds} component creates the following
four slots:

\begin{itemize}
\item \code{pos<n>_slot} (\code{Vec3Slot}) -- Position (in cm)
\item \code{angle<n>_slot} (\code{Vec3Slot}) -- Euler angles
\item \code{matrix<n>_slot} (\code{Mat3Slot}) -- Rotation matrix
\item \code{quat<n>_slot} (\code{QuatSlot}) -- Quaternion
\end{itemize}

where \code{<n>} is the number of the bird (1-based). Not all of the
slots are active at the same time. You can select which slot should
carry the corresponding value via the bird mode.

\begin{notice}[note]
To use the \class{FlockOfBirds} component the
\ulink{pySerial}{http://pyserial.sourceforge.net/} module has to be 
installed on your system.
\end{notice}

