% OBJMaterial

\section{\class{OBJMaterial} ---
         OBJ material}
\label{objmaterial}

The \class{OBJMaterial} class stores the parameters of materials
as specified in a MTL file (which is the material file that accompanies 
a Wavefront OBJ file).

\begin{classdesc}{OBJMaterial}{name = "OBJMaterial",\\ 
                               illum = 2,\\
                               Ka = (0.2, 0.2, 0.2),\\
                               Kd = (0.8, 0.8, 0.8),\\
                               Ks = (0.0, 0.0, 0.0),\\
                               Ke = (0.0, 0.0, 0.0),\\
                               Ns = 0.0,\\
                               Ni = 1.0,\\
                               d = 1.0,\\
                               Tr = 1.0,\\
                               Tf = (1.0, 1.0, 1.0),\\
                               sharpness = 0.0,\\
                               map_Ka = None,\\
                               map_Kd = None,\\
                               map_Ks = None,\\
                               map_Ke = None,\\
                               map_Ns = None,\\
                               map_d = None,\\
                               map_Bump = None,\\
                               density = 1.0\\
	                      }

\var{illum} sepcifies the illumination mode (0=constant, 1=diffuse, 2=diffuse+specular, ...).

\var{Ka} is the ambient color.

\var{Kd} is the diffuse color.

\var{Ks} is the specular color.

\var{Ke} is the emissive color.

\var{Ns} is the specular exponent (i.e. the shininess).

\var{Ni} is the index of reflection.

\var{d}, \var{Tr} and \var{Tf} are all transparency values. \var{d} and
\var{Tr} are given as floats and \var{Tf} as a color.

\var{sharpness}...

The \var{map_} arguments specify a texture map for the corresponding attribute.
The value must be a \class{OBJTextureMap} object.

\end{classdesc}


%-----------------------
\subsection{\class{OBJTextureMap} --- Texture map definition for the OBJ material}

The \class{OBJTextureMap} class stores the parameters of texture maps
as specified in an MTL file.

\begin{classdesc}{OBJTextureMap}{filename,\\
                                 offset = (0,0,0),\\
                                 scale = (1,1,1),\\
                                 turb = (0,0,0),\\
                                 mm = (0.0, 1.0),\\
                                 clamp = False,\\
                                 blendu = True,\\
                                 blendv = True,\\
                                 bumpsize = None,\\
                                 refltype = None
                                }

\var{filename} is the name of the image map to use.

\var{offset} contains three floats that are added to the u, v and w texture
coordinates, i.e. the map is translated.

\var{scale} contains three floats that are used to scale the u, v and w 
texture coordinates, i.e. to scale the texture map.

\var{turb} specifies turbulence values.

\var{mm} is a 2-tuple (\var{bias}, \var{gain}) that is used to modify the
color values of the map.

\var{clamp}...

\var{blendu} and \var{blendv}...

\var{bumpsize} is a float that determines the size of the bumps in a bump map.

\var{refltype} is a string that is only used in combination with reflection
maps. The string determines how the image should be interpreted 
("sphere", ...).

\end{classdesc}
