% sloargs

\section{\class{sloargs} ---
         Interrogate shader parameters from compiled shaders}

This module can be used to query shader parameters from compiled shaders.
This is done by using the shared libraries that ship with the
RenderMan renderers which means you can only parse shaders if
you have the respective renderer installed on your system. The module has
built-in support for shaders compiled by PRMan, 3Delight, Aqsis and
Pixie. The module can be extended to support other renderers as well.

Usually, you don't have to use this module explicitly as it is used internally
by the \module{slparams} module which is the main module for querying shaders.

% slparams
\begin{funcdesc}{slparams}{shader}
Read shader parameters (see the \function{slparams.slparams()}).
\end{funcdesc}

% getSloLib
\begin{funcdesc}{getSloLib}{sloSuffix}
Return the library name that manages a particular type of compiled shaders.
\var{sloSuffix} is the suffix of the compiled shaders.
The return value is the library name that is used to read the parameters
from compiled shaders of the given suffix. When called before a shader
was parsed, the return value is the library name that will be used when
the library is loaded. This value can be set by calling
\function{setSloLib()}. When the function is called after a shader was already parsed, the
return value is the absolute path to the actual library that is used
to read parameters.
\end{funcdesc}

% setSloLib
\begin{funcdesc}{setSloLib}{sloSuffix, libName}
Set the library name that should be used for reading shader parameters.
Shaders with the suffix \var{sloSuffix} (case-insensitive) will be handled by
the library \var{libName}. This function has no effect if a shader
of the given suffix has already been read. You must call this function at the beginning
of your application when \function{slparams()} hasn't been called yet.
\end{funcdesc}

% registerSloArgs
\begin{funcdesc}{registerSloArgs}{sloSuffix, sloArgsCls}
Register a SloArgs class for a particular renderer.
\var{sloSuffix} is the suffix (without dot) that is used for the compiled
shaders of this renderer. \var{sloArgsCls} is the SloArgs class that
can read compiled shaders for this renderer.
\end{funcdesc}
